---
title: "R Notebook"
output: html_document
---

```{r}
suppressMessages(library("vsn"))
suppressMessages(library("ggplot2"))
suppressMessages(library("tidyverse"))
data("kidney")
```

## Trying out with LC Data

Running section 2 from the [official `vsn` tutorial](https://bioconductor.org/packages/release/bioc/vignettes/vsn/inst/doc/A-vsn.html#assessing-the-performance-of-vsn). 

* The data consists of 168 metabolites, 12 samples and 2 groups (6 samples per group). Groups are generically named "treatment" and "control".
* The point of this vignette is just to see if mean and sd of each metabolite are correlated (as it turns out, they are). If so, normalize this correlation such that they are un-correlated (Student's t-test requires mean and s.d. to be independent). 


```{r}
# read data
tbl0 <- read_csv("/Users/don/Documents/my_vignettes/data/test_dme_data.csv") %>% replace(is.na(.), 0)

# Make `ExpressionSet` object
m <- as.matrix(tbl0 %>% dplyr::select(-c("Sample", "Group")))
rownames(m) <- as.vector(unlist(tbl0$Sample))
my_data <- object<-new("ExpressionSet", exprs=t(m))
```

mean and sd of each metabolite are indeed positively correlated:

```{r}
# meanSdPlot() un-normalized data
meanSdPlot(my_data, rank=TRUE)
```

Now to normalize and inspect with meanSdPlot again:

```{r}
# Normalize and meanSdPlot() data
xnorm <- justvsn(my_data)
meanSdPlot(xnorm, rank=TRUE)
```

Preview normalized data:
```{r}
head(exprs(xnorm))
```

